stats-project

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

stepwise_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=stepwise_predictions)
stepwise_submission
write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
```

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
```

@@

bw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=bw_predictions)
bw_submission
write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
```

>>>>

stepwise_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=stepwise_predictions)
stepwise_submission
#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
```

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
```

@@

bw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=bw_predictions)
bw_submission
#write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
```
